What the hell is the title of this paper?

### 2018-05-14 NIPS 2018/main.tex
added classic control results, mazes, images

\begin{figure*}[t]
  \begin{subfigure}[b]{0.15\textwidth}
    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=3cm, width=2.0cm]{images/maze/maze13.png}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
    \caption{}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
    \caption{}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
    \caption{}
  \end{subfigure}
  \caption{(a) Sample Maze, (b) transfer from $10$ sources in Cartpole, (c) transfer from $10$ source tasks in Mountain Car, and (d) transfer from $10$ sources in Mazes 0, 6, 13---see App. \ref{}}
  \label{fig:ccmazeplots}
\end{figure*}

To evaluate the performance of our transfer algorithms in more common benchmarks, we chose to use the well-known classic control environments: Cartpole and Mountain Car as defined in \citep{sutton1998reinforcement}. In the case of Cartpole we generated $20$ source tasks by uniformly sampling the cart mass, the pole mass and length. Instead, for Mountain Car, we generated the $20$ sources by uniformly sampling the base speed of the car. We kept a discount factor of $\gamma=0.99$ for both environments. Moreover, to train the source tasks we chose to use a Multilayer Perceptron (MLP) as approximator. We trained all source tasks until convergence and to transfer, in both settings, we used GVT and 1-MGVT choosing randomly $10$ of the trained sources.

In Fig. \ref{}, we show the results of transfer in Cartpole from which it is easily noticed a near-optimal jump-start in both GVT and 1-MGVT that during the following iterations converges to the optimal performance. In the other hand, transfer in Mountain Car as shown in Fig. \ref{}, a more complicated task than Cartpole, causes GVT to struggle to solve the target task but 1-MGVT reaches convergence within the same number of iterations to the optimal performances.

@@

For this setting we propose a maze environment, such as those in Fig. \ref{}, for a robotic agent to navigate. We created a set of 20 mazes of size $10\times10$ with continuous space within which we ensured four groups: each group with the goal position in one of the corners of the maze. In order to simulate a robotic agent, we set an action space that allows to control the linear and angular motion by a fixed distance of $0.5$ (\emph{move forward}) and a fixed angle of $\pm 22.5º$ (\emph{rotate counter- and clockwise}). Moreover, we enhanced the state space to include, in addition to the absolute position and orientation, a set of distance measures to the nearest obstacles from the agent's perspective with maximum range of $2$ and a field of vision from $-90º$ to $90º$ relative to its orientation. In this way, we provide the agent with information that a robot would normally collect from LIDARs, sonars and other sensors alike. Finally, in the same field of perception, we provide a boolean vector indicating whether the goal is within the range of observation. Regarding rewards, the agent gets 1 whenever it enters the goal area and 0 in any other situation and the MDP has a discount factor of $\gamma = 0.99$.

The main motivation for this set-up is that a robot is able to exploit locally-sensed information in addition to its estimation of the actual position---as opposed to the Rooms problem presented above---and it is such information that the robotic agent could learn to use and, also, exploit in different maze configurations leveraging its previous experience. Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting very good to assess how robust our algorithm is to negative transfer.

In App \ref the mazes used are enumerated. These were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with a multilayer perceptron with hidden layers $32\times32$  and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm. Finally, the MGVT algorithm, with one component for the posterior distribution, was used to solve the target tasks shown in Fig. *.

>>>>

\begin{figure*}[t]
  \begin{subfigure}[b]{0.15\textwidth}
    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=3cm, width=2.0cm]{images/maze/maze6.png}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
    \caption{}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
    \caption{}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev.pdf}
    \caption{}
  \end{subfigure}
  \caption{(a) Sample Maze (Maze 6), (b) transfer from $10$ sources in Cartpole, (c) transfer from $10$ source tasks in Mountain Car, and (d) transfer from $10$ sources in Mazes 6 and 13---see App. \ref{}.}
  \label{fig:ccmazeplots}
\end{figure*}

To evaluate the performance of our transfer algorithms in more common benchmarks, we chose to use the well-known classic control environments: Cartpole and Mountain Car as defined in \citep{sutton1998reinforcement}. In the case of Cartpole we generated $20$ source tasks by uniformly sampling the cart mass, the pole mass and length. Instead, for Mountain Car, we generated the $20$ sources by uniformly sampling the base speed of the car. We kept a discount factor of $\gamma=0.99$ for both environments. Moreover, to train the source tasks we chose to use a Multilayer Perceptron (MLP) as approximator. We trained all source tasks until convergence and to transfer, in both settings, we used GVT and 1-MGVT choosing randomly $10$ of the trained sources. Analogously to Sec. \ref{sec:gw}, in Fig. \ref{} and \ref{} we show the expected return---as the average of the last $50$ episodes of lerning---of transfer for $20$ independent runs randomizing the sources and target tasks. In Fig. \ref{}, that corresponds to Cartpole, it is easily noticeable a near-optimal jump-start, in both GVT and 1-MGVT, that during the following iterations converges to the optimal performance. Furthermore, transfer in Mountain Car as shown in Fig. \ref{}, a more complicated task than Cartpole, causes GVT to struggle to solve the target task but 1-MGVT reaches convergence, within the same number of iterations, to the optimal performances.

@@

For this setting we propose a maze environment, such as those in Fig. \ref{}, for a robotic agent to navigate. We created a set of 20 mazes---see App \ref{}---of size $10\times10$ with continuous space within which we ensured four groups: each group with the goal position in one of the corners of the maze. In order to simulate a robotic agent, we set an action space that allows to control the linear and angular motion by a fixed distance of $0.5$ (\emph{move forward}) and a fixed angle of $\pm 22.5º$ (\emph{rotate counter- and clockwise}). Moreover, we enhanced the state space to include, in addition to the absolute position and orientation, a set of distance measurements to the nearest obstacles from the agent's perspective with maximum range of $2$ and a field of vision of $9$ equally-spaced directions in $[-90,90º]$ relative to its orientation. In this way, we provide the agent with information that a robot would normally collect from LIDARs, sonars and other sensors alike. Finally, in the same field of perception, we provide a boolean vector indicating whether the goal is within the range of observation. Regarding rewards, the agent gets 1 whenever it enters the goal area and 0 in any other situation and the MDP has a discount factor of $\gamma = 0.99$.

The main motivation for this set-up is that a robot is able to exploit locally-sensed information in addition to its estimation of the actual position---as opposed to the Rooms problem presented above---and it is such information that the robotic agent could learn to use and, also, exploit in different maze configurations leveraging its previous experience. Moreover, simple variations in the maze structure could, potentially, produce big differences in the value function with respect to the ones seen in previous tasks which makes the setting suitable to assess how robust our algorithm is to negative transfer.

The mazes were solved using Deep Q Networks (DQN) [] \todo{cite DQN?} with an MLP with hidden layers $32\times32$ and, in order to perform the knowledge transfer, the target maze would be excluded from the source tasks given to the algorithm. Finally, the 1-MGVT algorithm was used to solve the target tasks---Mazes 6 and 13. As before, $20$ independent runs with randomized sources to transfer are averaged and shown in Fig. \ref{}, in this case $5$ source tasks were used for each trial. While these mazes pose a challenge for our algorithm, we can see that 1-MGVT is capable to still capture useful information from the sources and adapt to the target mazes which is demonstrated by the increased slope in the learning curve. \todo{actually, decide how to improve these results}
